---
title: 'A data-driven analysis for our start-up: INNOvALGAE'
author: "Corrado Alessio"
output: ioslides_presentation
fig_width: 8
fig_height: 5
fig_align: center
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)

#remotes::install_github("ianmoran11/mmtable2")

library(readxl)
library(tidyverse)
library(dplyr)
library(tidytext)
library(igraph)
library(ggwordcloud)
library(ggraph)
library(DT)

custom_stop = data.frame (
  word  = c("1", "2", "3", "4", "5", "10", "it's", "."),
  lexicon = "custom"
)

stop_words = rbind(stop_words, custom_stop)


#ogni file rappresenta un tema
list_of_files = list.files(path = "out",
                            recursive = TRUE,
                            pattern = "\\.csv$",
                            full.names = TRUE)

#tutti gli articoli caricati
df = list_of_files %>%
    set_names() %>% 
    map_df(read_csv, .id = "file_name")

#parole del testo
df_words = unnest_tokens(tbl = df, output = word, input = text)%>%
  anti_join(stop_words)

#parole del titolo
df_words_title = unnest_tokens(tbl = df, output = word, input = text)%>%
  anti_join(stop_words)

#bigrammi del testo
df_bigram = df %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
  filter(!is.na(bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  unite(bigram, word1, word2, sep = " ")

df_words_title_summary = df_words_title %>% group_by(word) %>% count(sort=TRUE) %>% ungroup()

df_words_summary = df_words %>% group_by(word, theme) %>% count(sort=TRUE) %>% ungroup()

df_words_tfidf = df_words %>%
  count(theme, word) %>%
  bind_tf_idf(word, theme, n) %>%
  arrange(desc(tf_idf))

df_bigram_tfidf = df_bigram %>%
  count(theme, bigram) %>%
  bind_tf_idf(bigram, theme, n) %>%
  arrange(desc(tf_idf))

df_themes = df %>% group_by(theme) %>% count() %>% ungroup() %>%
  mutate(name=paste("theme:", theme), type="theme", color="yellow", label=paste(theme, " (", n ,")", sep = ""))

df_keywords = df %>% group_by(keywords) %>% count() %>% ungroup() %>%
  mutate(name=paste("keyword:", keywords), type="keyword", color="orange", label=paste(keywords, " (", n ,")", sep = "")) 

df_connections = df %>% group_by(theme, keywords) %>% count() %>% ungroup()

wordCloud = function(theme_name = NA){

  data = rbind(
    df_words_tfidf %>% filter(is.na(theme_name) | theme==theme_name) %>% top_n(30) %>% select(tf_idf, label=word),
    df_bigram_tfidf %>% filter(is.na(theme_name) | theme==theme_name) %>% top_n(25) %>% select(tf_idf, label=bigram)
  ) %>% arrange(desc(tf_idf))
  
  
  ggplot(data, aes(label = label, size = tf_idf, color = factor(sample.int(30, nrow(data), replace = TRUE)))) +
    geom_text_wordcloud_area() +
    scale_size_area(max_size= 20) +
    theme_minimal()

}

```


## Have you ever wandered about the consequences of using chemical colors? 

Two of the main industries where they are used are *cosmetics* and *textiles*.

The main danger from the use of these artificial colors are *wastewaters*: rich of dangerous substances like toxins and heavy metals. 

These waters end up in sea and rivers, and consequentely in the food we eat. 

When it comes to *cosmetic products*, safety concerns are rising: they can directly alter the skin, causing toxic effects on the long term. 


## Solution: the use of biologic molecules

Natural molecules can avoid us the use of chemical colorants. 

One of them, *Phycocyanin*, is the only blue dye found in nature. 

Phycocyanin can be extracted from a microalgae: Spirulina. 

Spirulina and Phycocyanin have several beneficial properties on our organism. They are also eco-friendly, free of waste and their production absorbs CO2 from the environment. 

This is the reason why we are launching our start-up: *INNOvALGAE*. 


## Goal of this research

The goal of this research is to find informations on the *common sentiment* about sustainability, climate change, chemical colorants and Spirulina/Phycocyanin.

These informations will help us evaluate the current situation, find cues about customers' beliefs and guide our business decisions.


## Data collection 

We have build a set of interesting *keywords*, grouped by *themes*. 

Then we have fed the keywords to a *custom web crawler* which:

- searches the keywords in Google News;
- downloads a processes the articles;
- saves them to csv files. 

The crawler was written in Python, while the analysis was performed using R.


## Themes

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_themes %>% select(group=theme, value=n, label)

data = data %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(data$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

ggplot(data, aes(x="", y=prop, fill=group)) +
  geom_bar(stat="identity", width=1, color="white", alpha=0.8) +
  coord_polar("y", start=0) +
  theme_void() + 
  theme(legend.position="none", plot.title = element_text(hjust = 0.5)) +
  geom_text(aes(x=1.05, y = ypos, label = label), color = "white", size=4) +
  scale_fill_brewer(palette="Set1")
```

## Keywords

```{r warning=FALSE, message=FALSE, results='hide'}
  

ggplot(df_connections, aes(fill=keywords, y=n, x=theme)) + 
    geom_bar(position="dodge", stat="identity", color = "gray") +
    geom_text(aes(y=n + 4, label = keywords), color = "black", size=2.2, position = position_dodge(0.9)) +
    coord_flip() +
    xlab("") + ylab("") + 
    theme(legend.position="none", plot.title = element_text(hjust = 0.5)) 
```

## Searched Keywords

```{r warning=FALSE, message=FALSE, results='hide'}

vertices = rbind(
  df_themes %>% select(name, type, color, label, n), 
  df_keywords %>% select(name, type, color, label, n)
)

relations = df_connections %>% mutate(from=paste("theme:", theme), to=paste("keyword:", keywords), label=n) %>% select(from, to, label, n)

g = graph_from_data_frame(relations, directed = TRUE, vertices = vertices)

ggraph(g, layout = 'graphopt') + 
    geom_node_point(aes(size = 1* log(n, 2), color=color, alpha=0.2)) +
    geom_edge_link(aes(), 
                   arrow = arrow(type = "closed", length = unit(1, 'mm'))) + 
    geom_node_text(aes(label = label), size=2.5) +
  theme_graph() +
  theme(legend.position = "none")


```



## Overall sentiment

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words %>% inner_join(get_sentiments("bing")) %>%
  count(sentiment, sort = TRUE) %>%
  ungroup()

ggplot(data, aes(x = sentiment, y = n))+
  geom_col(aes(fill=sentiment)) +
  xlab("") + ylab("") +
  theme(plot.title = element_text(hjust = 0.5)) 
  
```


## Most common words in the titles

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words_title_summary %>% top_n(50, n) 

ggplot(data, aes(label = word, size = n, color = factor(sample.int(30, nrow(data), replace = TRUE)))) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 20) +
  theme_minimal()

```




## Sustainability

Nowdays, *sustainability is a priority*.

Let's have an overview about the general sentiment about sustainability, and identify the major trends. 


## 


```{r warning=FALSE, message=FALSE, results='hide'}


wordCloud("sustainability")

```



## Most common words about sustainability


```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words %>% filter(theme=="sustainability") %>% inner_join(get_sentiments("loughran")) %>%
  count(sentiment, sort = TRUE) %>%
  ungroup()

ggplot(data, aes(x = sentiment, y = n))+
  geom_col(aes(fill = sentiment)) +
  theme(legend.pos = "none") +
  xlab("") + ylab("Word count")

```



## Most negative articles


```{r warning=FALSE, message=FALSE}

data = df_words %>% filter(theme=="sustainability") %>% 
  inner_join(get_sentiments("loughran"), by = "word") %>%
  count(sentiment, title) %>%
  spread(sentiment, n, fill = 0) %>%
  filter(positive + negative > 50) %>% 
  mutate(score = (positive - negative) / (positive + negative)) %>% 
  drop_na(score) %>% 
  arrange(score) %>% select(title, positive, negative, score)
  


datatable(data) %>% formatStyle(columns = c(1,2,3,4,5,6,7), fontSize = '40%')

```


## Words per sentiment


```{r warning=FALSE, message=FALSE, results='hide'}

df_words %>% filter(theme=="sustainability") %>% 
  count(word) %>%
  inner_join(get_sentiments("loughran"), by = "word") %>%
  group_by(sentiment) %>%
  top_n(5, n) %>%
  ungroup() %>%
  mutate(word = reorder(word, n), fill=sentiment) %>%
  ggplot(aes(word, n, fill=fill)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~ sentiment, scales = "free") +
  theme(legend.pos = "none") + xlab("") + ylab("")
  

```



## Chemical colorants

Focussing on our target, *chemical colorants*, let's take a deeper look about the opinion of the crowd. 


## 

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words_summary %>% filter(theme == "chemical colorants") %>% top_n(50, n)

ggplot(data, aes(label = word, size = n, color = factor(sample.int(30, nrow(data), replace = TRUE)))) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size= 20) +
  theme_minimal()

```


## Overall sentiment

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words %>% filter(theme=="sustainability") %>% inner_join(get_sentiments("afinn")) %>%
  count(value, sort = TRUE) %>%
  ungroup()

ggplot(data, aes(x = value, y = n))+
  geom_col(aes(fill = value)) +
  xlab("") + ylab("Number of words")
```

## Positive and negative words


```{r warning=FALSE, message=FALSE, results='hide'}


df_words %>% filter(theme=="sustainability") %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup() %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  xlab("") + ylab("") +
  coord_flip()

```




## Spirulina

One of the most famous microalgae, *Spirulina*, can be used to extract the only blue natural dye, called "Phycocyanin". 

Spirulina has also a lot of beneficial properties, and its cultivation absorbs CO2 from the athmosphere. 


## 

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words_summary %>% filter(theme == "spirulina") %>% top_n(50, n)

ggplot(data, aes(label = word, size = n, color = factor(sample.int(30, nrow(data), replace = TRUE)))) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size= 20) +
  theme_minimal()


```




## Overall sentiment



```{r warning=FALSE, message=FALSE, results='hide'}
data = df_words %>% filter(theme=="spirulina") %>% inner_join(get_sentiments("nrc")) %>%
  count(sentiment, sort = TRUE) %>%
  ungroup()

ggplot(data, aes(x = sentiment, y = n))+
  geom_col(aes(fill = sentiment)) +
  theme(legend.pos = "none") +
  xlab("") + ylab("Number of words")
```


## Most common words per sentiment


```{r warning=FALSE, message=FALSE, results='hide'}

df_words %>% filter(theme=="spirulina") %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup() %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  xlab("") + ylab("") +
  coord_flip()

```


## Bigrams in most articles


```{r warning=FALSE, message=FALSE}

datatable(
  df_bigram %>% 
    filter(theme=="spirulina") %>%
    select(bigram, title) %>% distinct() %>% 
    count(bigram, sort = TRUE) %>% 
    filter(n > 20) %>% select(bigram, "Number of articles"=n)
)

```




## Steel Production

We plan to cultivate spirulina *using the CO2 and heat emitted by steel plants*. 

In this way, we can transform a waste into resource! 


## 

```{r warning=FALSE, message=FALSE, results='hide'}

wordCloud("steel production")

```


## Titles of articles about steel production



```{r warning=FALSE, message=FALSE}

data = df_words %>% filter(theme=="steel production") %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, title) %>%
  spread(sentiment, n, fill = 0) %>%
  filter(negative + positive > 100) %>% 
  mutate(score = (positive - negative) / (positive + negative)) %>% 
  drop_na(score) %>% 
  arrange(desc(score))
  
datatable(data) %>% formatStyle(columns = c(1,2,3,4,5,6,7), fontSize = '40%')

```




## Phycocyanin

Finally, here out product: *Phycocyanin*.

We believe that it will revolution the colorants industry, challenging climate change and preserving people's health.


##

```{r warning=FALSE, message=FALSE, results='hide'}

data = df_words_summary %>% filter(theme == "phycocyanin") %>% top_n(80, n)

ggplot(data, aes(label = word, size = n, color = factor(sample.int(30, nrow(data), replace = TRUE)))) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size= 20) +
  theme_minimal()


```



## Common sentiment about phycocyanin vs all


```{r warning=FALSE, message=FALSE, results='hide'}
data_phy = df_words %>% filter(theme=="phycocyanin") %>% inner_join(get_sentiments("loughran")) 

data_phy = data_phy %>%
  count(sentiment, sort = TRUE) %>%
  ungroup() %>% mutate(n = n / nrow(data_phy), label="phycocyanin")

data_all = df_words %>% inner_join(get_sentiments("loughran")) 

data_all = data_all %>%
  count(sentiment, sort = TRUE) %>%
  ungroup() %>% mutate(n = n / nrow(data_all), label="all")

data = rbind(data_phy, data_all)

ggplot(data, aes(x = sentiment, y = n * 100))+
  geom_col(aes(fill = label), position="dodge") +
  xlab("") + ylab("% of words")
```




## Titles of articles about phycocyanin



```{r warning=FALSE, message=FALSE}

data = df_words %>% filter(theme=="phycocyanin") %>%
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, title) %>%
  spread(sentiment, n, fill = 0) %>%
  filter(negative + positive > 100) %>% 
  mutate(score = (positive - negative) / (positive + negative)) %>% 
  drop_na(score) %>% 
  arrange(desc(score))
  
datatable(data) %>% formatStyle(columns = c(1,2,3,4,5,6,7), fontSize = '40%')

```


## Top bigrams


```{r warning=FALSE, message=FALSE, results='hide'}
df_bigram %>% 
  filter(theme=="phycocyanin") %>%
  select(bigram, title) %>% distinct() %>% 
  count(bigram, sort = TRUE) %>% 
  top_n(10) %>% 
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(x = bigram, y = n)) +
  geom_col(aes(fill=bigram)) +
  theme(legend.pos = "none")+
  coord_flip() +
  xlab("") + ylab("")

```


## Global positivity score


```{r}

data = df_words %>%
  inner_join(get_sentiments("loughran"), by = "word") %>%
  count(sentiment, theme) %>%
  spread(sentiment, n, fill = 0)

data %>%
  # positive score normalized by number of words
  mutate(score = (positive - negative) / (positive + negative)) %>%
  mutate(theme = reorder(theme, score)) %>%
  ggplot(aes(theme, score, fill = score > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("") + xlab("Positivity score")

```


## Thanks for your attention

<span style="color:red">We</span> <span style="color:forestgreen">are</span> <span style="color:blue;font-weight:bold">*InnoValgae*</span>.

<span style="color:chocolate">Come</span> <span style="color:darkolivegreen1">and</span> <span style="color:darkturquoise">join</span> <span style="color:orange1">our</span> <span style="color:magenta">*promising*</span>  <span style="color:blue;font-weight:bold">*blue*</span> <span style="color:seagreen">*future*</span>. 









